---
title: "p8105_hw6_jz3573"
output: github_document
date: "2023-12-02"
---

```{r setup}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library (readr)
library(viridis)
library(ggplot2)
set.seed(1)
```

# Problem 1 

## import data
```{r import data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
## generate 5000 bootstrap samples
```{r build bootsample function}
boot_sample = function(df) {
  sample_frac(df, replace=TRUE)
}
```

```{r draw 5000 samples}
boot_straps = 
  tibble(strap_number = 1:5000) %>% 
  mutate(
    strap_sample = map (strap_number, \(i) boot_sample(weather_df))
  )
set.seed(1)
```

## make a linear regression model 
```{r make a linear regression model }
boot_lr=
  boot_straps %>% 
  mutate(
    models = map (.x= strap_sample, ~ lm (tmax ~ tmin + prcp, data= .x )),
    glance = map (models, broom::glance),
    results = map (models, broom :: tidy),
    r_squared = map (glance, \ (df) pull (df, r.squared)),
    log = map(results, \(df) log(abs(df$estimate[2] * df$estimate[3])))
  )  %>% 
  select(strap_number, r_squared, log) |>
  mutate(
    r_squared = as.numeric(r_squared),
    log = as.numeric(log)
  )
    
  
```

## plot the distribution of estimates of r-square 
```{r distribution of r-square}
boot_lr %>% 
  ggplot (aes(x=r_squared)) +
  geom_density() +
  labs(title = "distribution of r-square")
```
The distribution of r_square is centered between 0.90 and 0.94, which means that the perception and tmin can predicts more than 90 % of tmax. In antoher word, the model is a good predicion model. 

## plot the distribution of estimate of log(b1*b2)

```{r plot the distribution of log(b1*b2)}
boot_lr %>% 
  ggplot (aes(x=log)) +
  geom_density() +
  labs (title = "distribution of log(b1*b2)" )
  

```
The distribution of log (b1*b2) is left-skewed and is centered around -5 

##  95% confidence interval for r_square 
```{r 95 CI for r_square}
boot_lr %>% 
  summarize (
    r_squared_2.5 = quantile (r_squared, 0.025),
    r_squared_97.5 = quantile (r_squared, 0.9725)
  ) %>% 
  knitr::kable (digits = 3)
```
 The 95% confidence interval for r_square is (0.889, 0.940)
 
##  95% confidence interval for log(b1*b2) 
```{r 95 CI for log(b1*b2)}
boot_lr %>% 
  summarize (
    log_2.5 = quantile(log,0.025),
    log_97.5 = quantile(log, 0.975)
  ) %>% 
  knitr::kable (digits = 3)
```
 The 95% confidence interval for r_square is (-8.589, 4.592)